\section{Alternative quadrotor platforms to the DJI Matrice 100, due to DOD restrictions on DJI products (J.~Lim)}
\label{sec:alternativequads}

With the main problems of the DJI Matrice 100 being the fragile balance between payload and ample flight time, it is recommended that an alternative is a drone that is capable to flying up to \SI{45}{\minute} or more with payload attached to the drone. The following platforms that are larger than the DJI Matrice 100 are listed below:
\begin{enumerate}
\item \textbf{DJI Matrice 210 RTK V2.} The Matrice 210 RTK V2 is a new model that DJI has released but is still not out in the market currently. It is a quadcopter that operates with two TB55 batteries. The max payload the drone can carry is \SI{1.34}{\kilo\gram} ($\sim\SI{3}{\pound}$). Although the battery life is longer than the DJI matrice 100, it is still relatively short with a max flight time of \SI{24}{\minute} with max payload and \SI{34}{\minute} without payload. The drone has an ultrasonic sensor for hovering accuracy that operates from \SIrange{0.33}{16.4}{\foot}. 

\item \textbf{DJI Matrice 600 Pro.} The DJI Matrice 600 Pro is a six propeller drone that is widely used as the platform for large scale missions such as farming lands. With six TB48S batteries, the Matrice 600 is capable of flying with a \SI{5.5}{\kilo\gram} payload for \SI{18}{\minute} and can fly without a payload for \SI{38}{\minute}.
\end{enumerate}

Unfortunately, both identified platforms are DJI projects which will soon be subject to more extensive DOD bans and are not being recommended for future USNA procurement. 